Bayesian Hierarchical Modeling: An Introduction and Reassessment

### 2022-06-10 D - Tutorial Normal Model brms/Online Supplement D - Bayesian Hierarchical Modeling in brms.Rmd
Updates

We have already estimated the model and saved it in the R object `brmsmodelfit_final`. In case you do not want to wait until the model has been fitted but continue immediately with the rest of this tutorial, you can load this R object that contains the model estimations.  
&nbsp;

\scriptsize 
```{r loadmodelfit, eval = FALSE}
model_fit <- readRDS(file = "myPath/brmsmodelfit_final.rds")

# For model comparison - sample_prior was set to "yes" 
model_fit_bf <- readRDS("myPath/brmsmodelfit_BF_final.rds")

@@

\scriptsize 
```{r loadmodelfits, show = FALSE}
model_fit <- readRDS(file = "/Users/myrtheveenman/Documents/GitHub/multilevel-tutorial-paper/R objects/brms/Truncated/BRMSmodelfit18_03012022.rds")

# For model comparison - sample_prior was set to "yes" 
model_fit_bf <- readRDS("/Users/myrtheveenman/Documents/GitHub/multilevel-tutorial-paper/R objects/brms/Truncated/BRMSmodelfit18_BF_03012022.rds")

>>>>

We have already estimated the model and saved it in the R object `brmmodel8_new03012022.rds`. In case you do not want to wait until the model has been fitted but continue immediately with the rest of this tutorial, you can load this R object that contains the model estimations.  
&nbsp;

\scriptsize 
```{r loadmodelfit, eval = FALSE}
model_fit <- readRDS(file = "myPath/brmmodel8_new03012022.rds")

# For model comparison - sample_prior was set to "yes" 
model_fit_bf <- readRDS("myPath/brmmodel8_new_bf_03012022l.rds")

@@

\scriptsize 
```{r loadmodelfits, show = FALSE, echo = FALSE}
setwd('..')
model_fit <- readRDS(file = "R objects/brms/Truncated/BRMSmodelfit18_03012022.rds")

# For model comparison - sample_prior was set to "yes" 
model_fit_bf <- readRDS("R objects/brms/Truncated/BRMSmodelfit18_BF_03012022.rds")

### 2022-06-10 F - Tutorial Log-Normal Model brms/Online Supplement F - Bayesian Hierarchical Modeling in brms - Log Model.Rmd
Updates

We have already estimated the model and saved it in the R object `brmslogmodelfit_final`. In case you do not want to wait until the model has been fitted but continue immediately with the rest of this tutorial, you can load this R object that contains the model estimations.  
&nbsp;

\scriptsize 
```{r loadmodelfit, eval = FALSE}
logmodel_fit <- readRDS(file = "myPath/brmslogmodelfit_final.rds")

# For model comparison - sample_prior was set to "yes" 
logmodel_fit_bf <- readRDS("myPath/brmslogmodelfit_BF_final.rds")

@@

\scriptsize 
```{r loadmodelfits, show = FALSE}
logmodel_fit <- readRDS(file = "/Users/myrtheveenman/Documents/GitHub/multilevel-tutorial-paper/R objects/brms/non-linear/brmmodel8log13012022.rds")

# For model comparison - sample_prior was set to "yes" 
logmodel_fit_bf <- readRDS("/Users/myrtheveenman/Documents/GitHub/multilevel-tutorial-paper/R objects/brms/BF/brmmodel8log26052022_bf.rds")

>>>>

We have already estimated the model and saved it in the R object `brmmodel8log13012022.rds`. In case you do not want to wait until the model has been fitted but continue immediately with the rest of this tutorial, you can load this R object that contains the model estimations.  
&nbsp;

\scriptsize 
```{r loadmodelfit, eval = FALSE}
logmodel_fit <- readRDS(file = "myPath/brmmodel8log13012022.rds")

# For model comparison - sample_prior was set to "yes" 
logmodel_fit_bf <- readRDS("myPath/BRMSmodelfit18_26052022_bf.rds")

@@

\scriptsize 
```{r loadmodelfits, show = FALSE, echo = FALSE}
setwd('..')
logmodel_fit <- readRDS(file = "R objects/brms/log-normal/brmmodel8log13012022.rds")

# For model comparison - sample_prior was set to "yes" 
logmodel_fit_bf <- readRDS("R objects/brms/BF/brmmodel8log26052022_bf.rds")
